---
title: Analyze the impact of covid-19 on offline Services Industry and Internet Services
  Industry
author: "Qian Feng"
date: "4/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Aim
The aim of this to........
## Package
```{r}
library(ggplot2)
library(dplyr)
library(arules)
library(arulesViz)
library(e1071)
library(gridExtra)
library(lubridate)
library(grid)
```

## Data
```{r}
original_uscovid <- read.csv("~/Desktop/daidai final/Qian Feng project/modify/modify_uscovid.csv")
uscovid<- na.omit(original_uscovid)
```

# Pre-processing
```{r}
uscovid$fatalityRate<-(uscovid$death/uscovid$positive)*100
uscovid$positiveRate<-(uscovid$positive/uscovid$totalTestResults)*100
uscovid$recoveryRate<-(uscovid$recovered/uscovid$positive)*100
uscovid$dailylevelnum<-(uscovid$positiveIncrease/uscovid$totalTestResultsIncrease)*100
uscovid$dailylevel.bracket<-discretize(uscovid$dailylevelnum, method = "frequency",breaks = 3,labels = c("bad","fine","good"))
```

## graph
```{r}
fatalityRate_graph<-ggplot(uscovid, aes(x=date,y=fatalityRate),color="red")+ geom_line()
positiveRate_graph<-ggplot(uscovid, aes(x=date,y=positiveRate),color="blue")+ geom_line()
recoveryRate_graph<-ggplot(uscovid, aes(x=date,y=recoveryRate),color="green")+ geom_line()

grid.arrange(fatalityRate_graph, positiveRate_graph,recoveryRate_graph)
ggplot(uscovid, aes(x=date, y=dailylevelnum, color=dailylevel.bracket)) + geom_line()


covid_graph<-ggplot(data=uscovid)+geom_line(aes(x=date,y=fatalityRate),color="red")+geom_line(aes(x=date,y=positiveRate),color="blue")+geom_line(aes(x=date,y=recoveryRate),color="green")

covid_graph

```
## subset
```{r}
#rule_uscovid<-subset(uscovid, select = c("date","fatalityRate", "positiveRate","recoveryRate","dailylevel.bracket")) 
rule_uscovid<-subset(uscovid, select = c("date","fatalityRate", "positiveRate","recoveryRate","dailylevelnum")) 

```
## rules
```{r}
#level_rules <- apriori(data = rule_uscovid, parameter = list (supp=0.001,conf = 0.08),list(rhs="dailylevelnum"))
level_rules <- apriori(data = rule_uscovid, parameter = list (supp=0.001,conf = 0.08))


```


## check
```{r}
#uscovid
#rule_uscovid
inspect(head(sort(level_rules, by = "lift"), 3))
```
## companydata
```{r}
zoom <- read.csv("~/Desktop/daidai final/Qian Feng project/modify/modify_zoom2.csv")
LasVegas <- read.csv("~/Desktop/daidai final/Qian Feng project/modify/modify_LasVegas2.csv")
Grubhub <- read.csv("~/Desktop/daidai final/Qian Feng project/modify/modify_Grubhub2.csv")
AMC <- read.csv("~/Desktop/daidai final/Qian Feng project/modify/modify_AMC2.csv")
```
## pre-possesing
```{r}
zoom_graph<-ggplot(zoom, aes(x=Date,y=Open))+ geom_line()
LasVegas_graph<-ggplot(LasVegas, aes(x=Date,y=Open))+ geom_line()
Grubhub_graph<-ggplot(Grubhub, aes(x=Date,y=Open))+ geom_line()
AMC_graph<-ggplot(AMC, aes(x=Date,y=Open))+ geom_line()

Allcompany_graph<-ggplot(NULL, aes(Date, Open)) + 
  geom_line(data = zoom, col = "red") +
  geom_line(data = LasVegas, col = "blue")+
  geom_line(data = Grubhub, col = "green")+
  geom_line(data = AMC, col = "black")

Allcompany_graph
```
## combine company with covid-19
fatalityRate_graph<-ggplot(uscovid, aes(x=date,y=fatalityRate),color="red")+ geom_line()
positiveRate_graph<-ggplot(uscovid, aes(x=date,y=positiveRate),color="blue")+ geom_line()
recoveryRate_graph<-ggplot(uscovid, aes(x=date,y=recoveryRate),color="green")+ geom_line()

zoom_graph<-ggplot(zoom, aes(x=Date,y=Open))+ geom_line()
LasVegas_graph<-ggplot(LasVegas, aes(x=Date,y=Open))+ geom_line()
Grubhub_graph<-ggplot(Grubhub, aes(x=Date,y=Open))+ geom_line()
AMC_graph<-ggplot(AMC, aes(x=Date,y=Open))+ geom_line()
```{r}
ggplot() +
      geom_line(data=uscovid, aes(x=date, y=fatalityRate), fill="red",
        colour="red", size=1 +
      geom_line(data=uscovid, aes(x=date, y=positiveRate), fill="blue",
        colour="blue", size=1) +
      geom_line(data=uscovid, aes(x=date, y=recoveryRate), fill="green",
        colour="green", size=1) +
      geom_line(data=zoom, aes(x=Date, y=Open), fill="black",
        colour="black", size=1),

  
```
## try
```{r}
zoom_try <- read.csv("~/Desktop/daidai final/Qian Feng project/zoom.csv")

```

```{r}
zoom_try$Date<- as.Date(zoom_try$Date,"%m/%d")
```

## output
```{r}
zoomtry_graph<-ggplot(zoom_try, aes(x=Date,y=Open))+ geom_line()
zoomtry_graph
zoomtry_graph2<-zoomtry_graph+ scale_x_date(date_breaks = "1 day"))
zoomtry_graph2

grid.newpage()
grid.draw(rbind(ggplotGrob(zoomtry_graph), ggplotGrob(zoomtry_graph2), size="last"))
```
## try2
```{r}
#ggplot(data=zoom_try[which(zoom_try$Date>"2020-9-30"),],
#       aes(x=Date, y=Open))+ geom_line()

start.date = as.Date("2020-09-30")
end.date   = as.Date("2020-12-04")

filtered = data=zoom_try %>% 
  filter(Date >= start.date & 
         Date <= end.date)

ggplot(filtered, aes(x=Date, y=Open)) + geom_line()
```

